Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-10-22 batchdedup/main.tex
revised

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
%\makeatletter
%\def\url@leostyle{%
%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%\makeatother
%% Now actually use the newly defined style.
%\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

\usepackage{pgfplots}
\pgfplotsset{compat=1.7}
\DeclareGraphicsExtensions{.pdf}

%pgfplots setup
\pgfplotsset{every axis/.append style={
	very thick,
	tick style={thick}}}
\pgfplotsset{
        every mark/.append style={solid}
}
\pgfplotscreateplotcyclelist{mcolor}{%
    {blue,every mark/.append style={fill=blue},mark=*},
    {red,every mark/.append style={fill=red},mark=square*},
    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}

@@

\newcommand{\comments}[1]{}

@@

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\
{\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
%University of California at Santa Barbara
%\and
%Hong Tang\\
%Alibaba Inc.
}

@@

\input{abs}
\input{intro} %introduce the vm cloud, backup problem, and our requirements
\input{background} %related works, related solutions, 
\input{arch} %, design considerations, architecture
%\input{analysis} %, design considerations, architecture
\input{eval} %data study, zipf, model of cds size and dedup efficiency
%\input{results}
%\input{related}
%\input{future}
\input{concl}

>>>>

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{listings}
%\lstset{language=C}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
%\makeatletter
%\def\url@leostyle{%
%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%\makeatother
%% Now actually use the newly defined style.
%\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

\usepackage{pgfplots}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

%pgfplots setup
\pgfplotsset{every axis/.append style={
	very thick,
	tick style={thick}}}
\pgfplotsset{
        every mark/.append style={solid}
}
%this is my preferred default cycle list for pgfplots.
\pgfplotscreateplotcyclelist{mcolor}{%
    {blue,every mark/.append style={fill=blue},mark=*},
    {red,every mark/.append style={fill=red},mark=square*},
    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}

@@

\newcommand{\comments}[1]{}
\newcommand{\todo}[1]{\textit{\color{red}#1}}

@@

\author{
Daniel Agun$^{\star}$,  
Wei Zhang$^{\star}$, and Tao Yang$^\star$ \\
{\normalsize$^\star$  University of California at Santa Barbara}, 
%{\normalsize$^\dagger$Alibaba Inc.}
%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
%University of California at Santa Barbara
%\and
%Hong Tang\\
%Alibaba Inc.
}

@@

\input{abs}
\input{intro} %introduce the vm cloud, backup problem, and our requirements
\input{background} %related works, related solutions, 
\input{arch} %, design considerations, architecture
\input{analysis} %, design considerations, architecture
\input{scheduling} % CoW cost considerations and round scheduling
\input{eval} %data study, zipf, model of cds size and dedup efficiency
%\input{results}
%\input{related}
%\input{future}
\input{concl}
